---
title: "AirBnB_datasets"
author: "Ellie Schmucker, with edits by Kayla Freeman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load in and process 2024 Datase4t

```{r}
library(tidyverse)
library(skimr)
library(stringr)
library(GGally)

nyc_2024 <- read.csv("nyc_mar2024.csv")


nyc_2024 <- nyc_2024 %>%
  select(id, name, host_id, host_name, neighborhood_overview, neighbourhood_cleansed, neighbourhood_group_cleansed,latitude, longitude, room_type, price, last_scraped, last_review, minimum_nights, number_of_reviews, last_review, reviews_per_month, reviews_per_month, calculated_host_listings_count, availability_365, number_of_reviews_ltm, license, host_location, host_since, host_neighbourhood, host_listings_count, host_total_listings_count,  number_of_reviews_l30d )
head(nyc_2024)

filtered_nyc_2024 <- nyc_2024 %>%
  mutate(last_review_date = as.Date(last_review)) %>%
  filter(last_review_date >= max(last_review_date, na.rm = T) %m-% months(6) ) %>% 
  rename(neighbourhood_group = neighbourhood_group_cleansed)
#
filtered_nyc_2024 %>% select(last_review_date) %>% summary()

head(filtered_nyc_2024$price)
```

## Price to Numeric

```{r}
filtered_nyc_2024$price <- (gsub("\\$", "", filtered_nyc_2024$price))
filtered_nyc_2024$price <- (gsub(",", "", filtered_nyc_2024$price))


filtered_nyc_2024$price = ifelse(filtered_nyc_2024$price == "", 0.00, filtered_nyc_2024$price)

filtered_nyc_2024$price = as.numeric(filtered_nyc_2024$price)

reg_df_2024 = filtered_nyc_2024 %>% select(room_type, price, minimum_nights, number_of_reviews, reviews_per_month, calculated_host_listings_count, availability_365,
                                           neighbourhood_group)
```

## One hot room type

```{r}
reg_df_2024 = reg_df_2024 %>% mutate(entire = ifelse(room_type == "Entire home/apt",1,0),
                                     private = ifelse(room_type == "Private room",1,0),
                                     shared = ifelse(room_type == "Shared room",1,0))
reg_df_2024$room_type = NULL
```


# Load in and process 2023 dataset

```{r}
nyc_2023 <- read.csv("nyc_2023.csv")

filtered_nyc_2023 <- nyc_2023 %>%
  mutate(last_review_date = as.Date(last_review)) %>%
  filter(last_review_date >= max(last_review_date, na.rm = T) %m-% months(6) )

filtered_nyc_2023$price = as.numeric(filtered_nyc_2023$price)

reg_df_2023 = filtered_nyc_2023 %>% select(room_type, price, minimum_nights, number_of_reviews, 
                                           reviews_per_month, calculated_host_listings_count,
                                           availability_365, neighbourhood_group)
```

## One hot room type

```{r}
reg_df_2023 = reg_df_2023 %>% mutate(entire = ifelse(room_type == "Entire home/apt",1,0),
                                     private = ifelse(room_type == "Private room",1,0),
                                     shared = ifelse(room_type == "Shared room",1,0))
reg_df_2023$room_type = NULL
```


# Exploration
## Heatmaps
### 2024

```{r}
#cor_matrix_2024 <- cor(reg_df_2024)

# Generate the heatmap
#heatmap(cor_matrix_2024, 
#        col = colorRampPalette(c("blue", "white", "red"))(50), 
#        scale = "none", 
#        main = "Heatmap of Correlations")
```

So that's not super helpful.

### 2023

```{r}
#cor_matrix_2023 <- cor(reg_df_2023)

# Generate the heatmap
#heatmap(cor_matrix_2023, 
#        col = colorRampPalette(c("blue", "white", "red"))(50), 
#        scale = "none", 
#        main = "Heatmap of Correlations")
```

Again, no strong correlations

# Regression

## Model 1 2024
```{r}
model_1_2024 = lm(price ~ ., data = reg_df_2024)
```

### Mod1 summary
```{r}
summary(model_1_2024)
```

### Stepwise selection
```{r}
stepwise_model_2024 <- step(model_1_2024, direction = "both")
```
#### stepwise2024 summary
```{r}
summary(stepwise_model_2024)
```

## Model 1 2023
```{r}
model_1_2023 = lm(price ~ ., data = reg_df_2023)
```

### Mod12023 summary
```{r}
summary(model_1_2023)
```

### Stepwise selection
```{r}
stepwise_model_2023 <- step(model_1_2023, direction = "both")
```

#### stepwise2023 summary
```{r}
summary(stepwise_model_2023)
```

## Model 2 2024
Dropping price outliers for this model
```{r}
reg_min_df_2024 = reg_df_2024 %>% filter(price <= 85000)

model_2_2024 = lm(price ~ ., data = reg_min_df_2024)
```

### Mod2 summary
```{r}
summary(model_2_2024)
```

### Stepwise
```{r}
stepwise_model2_2024 <- step(model_2_2024, direction = "both")
summary(stepwise_model2_2024)
```

## Model 2 2023

```{r}
reg_min_df_2023 = reg_df_2023 %>% filter(price <= 85000)

model_2_2023 = lm(price ~ ., data = reg_min_df_2023)
```

### Mod2 summary
```{r}
summary(model_2_2024)
```

### Stepwise
```{r}
stepwise_model2_2023 <- step(model_2_2023, direction = "both")
summary(stepwise_model2_2023)
```

# Notes So Far

It seems like the predictability of the models is better for 2023, with many of the 2023 significant variables in 2023, becoming insignificant in 2024

# Residual Checking
## Model 1 2024
```{r}
res_1_2024 = residuals(model_1_2024)
for (i in c(1:5)){
  plot(model_1_2024, which = i)
}
```

## Model 1 2024 step
```{r}
for (i in c(1:5)){
  plot(stepwise_model_2024, which = i)
}
```

## Model 2 2024
```{r}
for (i in c(1:5)){
  plot(model_2_2024, which = i)
}
```

## Model 2 2024 step
```{r}
for (i in c(1:5)){
  plot(stepwise_model2_2024, which = i)
}
```

## Model 1 2023
```{r}
for (i in c(1:5)){
  plot(model_1_2023, which = i)
}
```

## Model 1 2023 step
```{r}
for (i in c(1:5)){
  plot(stepwise_model_2023, which = i)
}
```

## Model 2 2023
```{r}
for (i in c(1:5)){
  plot(model_2_2023, which = i)
}
```

## Model 2 2023 step
```{r}
for (i in c(1:5)){
  plot(stepwise_model2_2023, which = i)
}
```


```{r}
min(fitted(model_1_2023))
```

# Model 3

```{r}
reg_fin_df_2024 = reg_min_df_2024 %>% 
  filter(price > 0)

model_3_2024 = glm(price ~ ., data = reg_fin_df_2024)

summary(model_3_2024)
```

```{r}
for (i in c(1:5)){
  plot(model_3_2024, which = i)
}
```

```{r}
reg_fin_df_2024$fitted = fitted(model_3_2024)
reg_fin_df_2024$residual = residuals(model_3_2024)
```

```{r}
stepwise_model3_2024 <- step(model_3_2024, direction = "both")
summary(stepwise_model3_2024)
```

# Load Clean Dfs:

```{r}
clean_post = read_csv("/Users/lukewilsen/Desktop/School/Stat_535/535_Project/clean_post.csv")
clean_post = clean_post %>% 
  select(room_type, price, minimum_nights, number_of_reviews, reviews_per_month,
         calculated_host_listings_count, availability_365,neighbourhood_group_cleansed) %>% 
  rename(neighbourhood_group = neighbourhood_group_cleansed) %>% 
  mutate(entire = ifelse(room_type == "Entire home/apt",1,0),
                                     private = ifelse(room_type == "Private room",1,0),
                                     shared = ifelse(room_type == "Shared room",1,0))

clean_post$room_type = NULL
clean_post$price <- (gsub("\\$", "", clean_post$price))
clean_post$price <- (gsub(",", "", clean_post$price))


clean_post$price = ifelse(clean_post$price == "", 0.00, clean_post$price)

clean_post$price = as.numeric(clean_post$price)

clean_pre = read_csv("/Users/lukewilsen/Desktop/School/Stat_535/535_Project/clean_pre.csv")
clean_pre = clean_pre %>% 
  select(room_type, price_2023, minimum_nights, number_of_reviews, reviews_per_month,
         calculated_host_listings_count, availability_365,neighbourhood_group) %>% 
  mutate(entire = ifelse(room_type == "Entire home/apt",1,0),
                                     private = ifelse(room_type == "Private room",1,0),
                                     shared = ifelse(room_type == "Shared room",1,0)) %>% 
  rename(price = price_2023)

clean_pre$room_type = NULL
```



# Model 4

```{r}
reg_m4_df_2024 = reg_fin_df_2024 %>% 
  filter(price > quantile(reg_fin_df_2024$price, 0.01),
         price < quantile(reg_fin_df_2024$price, 0.99))

reg_m4_df_2024$log_price = NULL
reg_m4_df_2024$sqrt_price = NULL
reg_m4_df_2024$fitted = NULL
reg_m4_df_2024$residual = NULL
reg_m4_df_2024$availability_365 = NULL


model_4_2024 = glm(log(price) ~ ., data = reg_m4_df_2024)

model_4_post = glm(log(price) ~ ., data = clean_post)

summary(model_4_2024)
summary(model_4_post)
```

```{r}
for (i in c(1:5)){
  plot(model_4_post, which = i)
}
```

```{r}
stepwise_model4_2024 <- step(model_4_2024, direction = "both")
summary(stepwise_model4_2024)
```

```{r}
for (i in c(1:5)){
  plot(stepwise_model4_2024, which = i)
}
```

## 2023 Model 4

```{r}
reg_m4_df_2023 =  reg_min_df_2023 %>% 
  filter(price > quantile(reg_min_df_2023$price, 0.01),
         price < quantile(reg_min_df_2023$price, 0.99))

reg_m4_df_2023$availability_365 = NULL

model_4_2023 = glm(log(price) ~ ., data = reg_m4_df_2023)
model_4_pre = glm(log(price) ~ ., data = clean_pre)

summary(model_4_2023)
summary(model_4_pre)
```

```{r}
for (i in c(1:5)){
  plot(model_4_pre, which = i)
}
```

```{r}
stepwise_model4_2023 <- step(model_4_2023, direction = "both")
```

```{r}
for (i in c(1:5)){
  plot(stepwise_model4_2023, which = i)
}
```

```{r}
summary(stepwise_model4_2023)
summary(stepwise_model4_2024)
```

# Model 4 coeff comparisons
```{r}

coefs_post = data.frame(
  estimates_post = format(round(coef(model_4_post), 4), scientific = FALSE),
  se_post = format(round(summary(model_4_post)$coefficients[, 2], 4), scientific = FALSE),
  P_post = summary(model_4_post)$coefficients[,4]
)


coefs_pre = data.frame(
  estimates_pre = round(coef(model_4_pre), 4),
  se_pre = round(summary(model_4_pre)$coefficients[, 2],4),
  P_pre = summary(model_4_pre)$coefficients[,4]
)

coef_compare = cbind(coefs_pre, coefs_post) %>% rownames_to_column(var = "Variable")
print(coef_compare)
```

```{r}
coef_wider = coef_compare %>% 
  mutate(estimates_post = as.numeric(estimates_post),
         se_post = as.numeric(se_post),
         P_post = as.numeric(P_post)) %>% 
  pivot_longer(cols = c(starts_with("estimates"), 
                        starts_with("se"), 
                        starts_with("P")),
                              names_to = c("Metric", "Year"),
               names_sep = "_",
                              values_to = "Value")%>%
  pivot_wider(
    names_from = Metric,
    values_from = Value
  )

z_value <- 1.96  # Z-value for 95% CI
coef_wider <- coef_wider %>%
  mutate(
    CI_lower = exp(estimates) - z_value * exp(se),
    CI_upper = exp(estimates) + z_value * exp(se),
    Variable = ifelse(Variable == "neighbourhood_groupBrooklyn", "ng_Brooklyn",
                      ifelse(Variable == "neighbourhood_groupManhattan", "ng_Manhattan",
                             ifelse(Variable == "neighbourhood_groupQueens", "ng_Queens",
                                    ifelse(Variable == "neighbourhood_groupStaten Island", "ng_Staten Island", Variable)))),
    estimates_exp = exp(estimates)
  )
```


```{r}
coef_wider %>% 
  filter(Variable != "(Intercept)") %>% 
  ggplot(aes(x = Variable, y = estimates_exp, color = Year, group = Year)) +
  geom_point(size = 1) +  # Points for the estimates
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2) +  # Error bars for confidence intervals
  theme_minimal() +
  labs(
    title = "95% Confidence Intervals for Estimates by Year and Variable",
    x = "Variable",
    y = "Estimate",
    color = "Year"
  )+
  theme(axis.text.x = element_text(angle = 45, vjust = , hjust=1))
```


```{r}
coef_wider %>% 
  filter(Variable == "(Intercept)") %>% 
  ggplot(aes(y = Variable, x = estimates_exp, color = Year, group = Year)) +
  geom_point(size = 4) +  # Points for the estimates
  geom_errorbar(aes(xmin = CI_lower, xmax = CI_upper), width = 0.2) +  # Error bars for confidence intervals
  theme_minimal() +
  labs(
    title = "95% Confidence Intervals for Estimates by Year and Variable",
    x = "Variable",
    y = "Estimate",
    color = "Year"
  )

```

# Bootstrapping!

```{r}
model_4_post = glm(log(price) ~ ., data = clean_post)
model_4_pre = glm(log(price) ~ ., data = clean_pre)

coefs_post = data.frame(
  estimates_post = format(round(coef(model_4_post), 4), scientific = FALSE),
  se_post = format(round(summary(model_4_post)$coefficients[, 2], 4), scientific = FALSE),
  P_post = summary(model_4_post)$coefficients[,4]
)


coefs_pre = data.frame(
  estimates_pre = round(coef(model_4_pre), 4),
  se_pre = round(summary(model_4_pre)$coefficients[, 2],4),
  P_pre = summary(model_4_pre)$coefficients[,4]
)

format(round(coef(model_4_post), 4), scientific = FALSE)

list(
  estimates_post = format(round(coef(model_4_post), 4), scientific = FALSE),
  se_post = format(round(summary(model_4_post)$coefficients[, 2], 4), scientific = FALSE),
  P_post = summary(model_4_post)$coefficients[,4]
     )
```


```{r}
#clean post bootstrap
n = nrow(clean_post)
M = 1000
estimate_list <- vector("list", length(names(coef(model_4_post))))
names(estimate_list) = names(coef(model_4_post))
for (i in 1:length(estimate_list)){
  estimate_list[[i]] = numeric(M)
}

#Bootstraps difference in estimates for the two years
for (m in 1:M) {
  bootstrap_sample_idx_1 <- sample(n, replace = TRUE) 
  bootstrap_sample_idx_2 = sample(n, replace = TRUE)
  btsp_post <- clean_post[bootstrap_sample_idx_1, ]
  btsp_pre = clean_pre[bootstrap_sample_idx_2, ]
  
  post_mod = glm(log(price) ~ ., data = btsp_post)
  pre_mod = glm(log(price) ~ ., data = btsp_pre)
  
  estimate_list$`(Intercept)`[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[1]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[1]]))
  
  estimate_list$minimum_nights[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[2]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[2]]))
  
  estimate_list$number_of_reviews[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[3]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[3]]))
  
  estimate_list$reviews_per_month[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[4]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[4]]))
  
  estimate_list$calculated_host_listings_count[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[5]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[5]]))
  
  estimate_list$availability_365[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[6]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[6]]))
  
  estimate_list$neighbourhood_groupBrooklyn[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[7]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[7]]))
  
  estimate_list$neighbourhood_groupManhattan[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[8]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[8]]))
  
  estimate_list$neighbourhood_groupQueens[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[9]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[9]]))
  
  estimate_list$`neighbourhood_groupStaten Island`[m] = (as.numeric(format(round(coef(post_mod), 4),scientific = FALSE)[[10]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[10]]))
  
  estimate_list$entire[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[11]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[11]]))
  
  estimate_list$private[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[12]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[12]]))
  
  estimate_list$shared[m] = (as.numeric(format(round(coef(post_mod), 4),
                                                  scientific = FALSE)[[13]]) - as.numeric(format(round(coef(pre_mod), 4),scientific = FALSE)[[13]]))
}

for (i in 1:length(estimate_list)){
  print(
    ggplot()+
      geom_histogram(aes(x = estimate_list[[i]]), color = "white")+
      geom_vline(xintercept = quantile(estimate_list[[i]], 0.025), color = "red")+
      geom_vline(xintercept = quantile(estimate_list[[i]], 0.975), color = "red")+
      ggtitle(names(estimate_list[i]))+
      xlab(names(estimate_list[i]))
    )
}

ggplot()+
  geom_histogram(aes(x = estimate_list[[1]]))
```
Practically significant: Min nights, # reviews, reviews per month, neighborhood = Brooklyn, neighborhood = Manhattan, room type = private, room type = shared
- These variables had estimated differences that were not equal to 0 at a 95% confidence level

```{r}
coef_change_sum = data.frame(variable = names(estimate_list),
           relative_change = numeric(length(names(estimate_list))),
           Bootstrapped_CI_L = numeric(length(names(estimate_list))),
           Bootstrapped_CI_U = numeric(length(names(estimate_list))),
           reject_null = character(length(names(estimate_list))))

for (i in 1:length(estimate_list)){
  cat("Variable:",names(estimate_list)[i], 
      "\n", 
      exp(mean(estimate_list[[i]])), "times relative change in the multiplicative effect of variable on price", "\n",
      "Bootstrapped estimate difference CI:", c(quantile(estimate_list[[i]], 0.025),
                                                quantile(estimate_list[[i]], 0.975)), "\n",
      ifelse((0 > quantile(estimate_list[[i]], 0.025)) & (0 < quantile(estimate_list[[i]], 0.975)), "Fail to Reject null", "Reject Null"),"\n",
      "Post law coefficient estimate:", (coef(model_4_post)[i]), "\n",
      "Pre law coefficient estimate:", (coef(model_4_pre)[i]), "\n")
  
  coef_change_sum$variable[i] = names(estimate_list)[i]
  coef_change_sum$relative_change[i] = exp(mean(estimate_list[[i]]))
  coef_change_sum$Bootstrapped_CI_L[i] = quantile(estimate_list[[i]], 0.025)
  coef_change_sum$Bootstrapped_CI_U[i] = quantile(estimate_list[[i]], 0.975)
  coef_change_sum$reject_null[i] = ifelse((0 > quantile(estimate_list[[i]], 0.025)) & (0 < quantile(estimate_list[[i]], 0.975)), "Fail to Reject null", "Reject Null")

}
```

```{r}
coef_change_sum %>% 
  mutate(percent_change = abs(coef_change_sum$relative_change - 1)) %>% filter(reject_null == "Reject Null" & percent_change > 0.05)

coef_change_sum
```



```{r}
ggplot() +
  geom_histogram(aes(x = exp(estimate_list$neighbourhood_groupBrooklyn)), color = "white") +
  geom_vline(xintercept = exp(quantile((estimate_list$neighbourhood_groupBrooklyn), 0.025)), color = "red") +
  geom_vline(xintercept = exp(quantile((estimate_list$neighbourhood_groupBrooklyn), 0.975)), color = "red") +
  geom_vline(xintercept = exp(mean(estimate_list$neighbourhood_groupBrooklyn)), lty = "dashed", color = "red") +
  annotate(
    "text",
    x = exp(mean(estimate_list$neighbourhood_groupBrooklyn)), # Position along x-axis
    y = 95, # Adjust based on the y-scale of your histogram
    label = paste0("Mean: ", round(exp(mean(estimate_list$neighbourhood_groupBrooklyn)), 2)),
    color = "red",
    hjust = -0.2
  ) +
  ggtitle(
    "BTSP Estimate of Relative Change in Multiplicative Effect",
    subtitle = "Variable: Located in Brooklyn (Binary)"
  ) +
  xlab("Brooklyn")+
  ylab("Count")

ggplot() +
  geom_histogram(aes(x = exp(estimate_list$neighbourhood_groupManhattan)), color = "white") +
  geom_vline(xintercept = exp(quantile((estimate_list$neighbourhood_groupManhattan), 0.025)), color = "red") +
  geom_vline(xintercept = exp(quantile((estimate_list$neighbourhood_groupManhattan), 0.975)), color = "red") +
  geom_vline(xintercept = exp(mean(estimate_list$neighbourhood_groupManhattan)), lty = "dashed", color = "red") +
  annotate(
    "text",
    x = exp(mean(estimate_list$neighbourhood_groupManhattan)), # Position along x-axis
    y = 95, # Adjust based on the y-scale of your histogram
    label = paste0("Mean: ", round(exp(mean(estimate_list$neighbourhood_groupManhattan)), 2)),
    color = "red",
    hjust = -0.2
  ) +
  ggtitle(
    "BTSP Estimate of Relative Change in Multiplicative Effect",
    subtitle = "Variable: Located in Manhattan (Binary)"
  ) +
  xlab("Manhattan")+
  ylab("Count")
    
ggplot() +
  geom_histogram(aes(x = exp(estimate_list$shared)), color = "white") +
  geom_vline(xintercept = exp(quantile((estimate_list$shared), 0.025)), color = "red") +
  geom_vline(xintercept = exp(quantile((estimate_list$shared), 0.975)), color = "red") +
  geom_vline(xintercept = exp(mean(estimate_list$shared)), lty = "dashed", color = "red") +
  annotate(
    "text",
    x = exp(mean(estimate_list$shared)), # Position along x-axis
    y = 95, # Adjust based on the y-scale of your histogram
    label = paste0("Mean: ", round(exp(mean(estimate_list$shared)), 2)),
    color = "red",
    hjust = -0.2
  ) +
  ggtitle(
    "BTSP Estimate of Relative Change in Multiplicative Effect",
    subtitle = "Variable: Room Type = Shared (Binary)"
  ) +
  xlab("Shared")+
  ylab("Count")

ggplot() +
  geom_histogram(aes(x = exp(estimate_list$private)), color = "white") +
  geom_vline(xintercept = exp(quantile((estimate_list$private), 0.025)), color = "red") +
  geom_vline(xintercept = exp(quantile((estimate_list$private), 0.975)), color = "red") +
  geom_vline(xintercept = exp(mean(estimate_list$private)), lty = "dashed", color = "red") +
  annotate(
    "text",
    x = exp(mean(estimate_list$private)), # Position along x-axis
    y = 95, # Adjust based on the y-scale of your histogram
    label = paste0("Mean: ", round(exp(mean(estimate_list$private)), 2)),
    color = "red",
    hjust = -0.2
  ) +
  ggtitle(
    "BTSP Estimate of Relative Change in Multiplicative Effect",
    subtitle = "Variable: Room Type = Private (Binary)"
  ) +
  xlab("Private")+
  ylab("Count")
```




!BRONX IS REF GROUP!
- dropped "Entire" from 2023 and 2024 model
  - Not significant for either (so can basically assume 3 levels to room type????)
  
Double check whether availability 365 is worth including

Bootstrap results

Show best model, talk about all the other models I tried

