---
title: "AirBnB_datasets"
author: "Ellie Schmucker, with edits by Kayla Freeman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load in and process 2024 Datase4t

```{r}
library(tidyverse)
library(skimr)
library(stringr)
library(GGally)

nyc_2024 <- read.csv("nyc_mar2024.csv")


nyc_2024 <- nyc_2024 %>%
  select(id, name, host_id, host_name, neighborhood_overview, neighbourhood_cleansed, neighbourhood_group_cleansed,latitude, longitude, room_type, price, last_scraped, last_review, minimum_nights, number_of_reviews, last_review, reviews_per_month, reviews_per_month, calculated_host_listings_count, availability_365, number_of_reviews_ltm, license, host_location, host_since, host_neighbourhood, host_listings_count, host_total_listings_count,  number_of_reviews_l30d )
head(nyc_2024)

filtered_nyc_2024 <- nyc_2024 %>%
  mutate(last_review_date = as.Date(last_review)) %>%
  filter(last_review_date >= max(last_review_date, na.rm = T) %m-% months(6) )
#
filtered_nyc_2024 %>% select(last_review_date) %>% summary()

head(filtered_nyc_2024$price)
```

## Price to Numeric

```{r}
filtered_nyc_2024$price <- (gsub("\\$", "", filtered_nyc_2024$price))
filtered_nyc_2024$price <- (gsub(",", "", filtered_nyc_2024$price))


filtered_nyc_2024$price = ifelse(filtered_nyc_2024$price == "", 0.00, filtered_nyc_2024$price)

filtered_nyc_2024$price = as.numeric(filtered_nyc_2024$price)

reg_df_2024 = filtered_nyc_2024 %>% select(room_type, price, minimum_nights, number_of_reviews, 
                                           reviews_per_month, calculated_host_listings_count,
                                           availability_365)
```

## One hot room type

```{r}
reg_df_2024 = reg_df_2024 %>% mutate(entire = ifelse(room_type == "Entire home/apt",1,0),
                                     private = ifelse(room_type == "Private room",1,0),
                                     shared = ifelse(room_type == "Shared room",1,0),
                                     hotel = ifelse(room_type == "Hotel room",1,0))
reg_df_2024$room_type = NULL
```


# Load in and process 2023 dataset

```{r}
nyc_2023 <- read.csv("nyc_2023.csv")

filtered_nyc_2023 <- nyc_2023 %>%
  mutate(last_review_date = as.Date(last_review)) %>%
  filter(last_review_date >= max(last_review_date, na.rm = T) %m-% months(6) )

filtered_nyc_2023$price = as.numeric(filtered_nyc_2023$price)

reg_df_2023 = filtered_nyc_2023 %>% select(room_type, price, minimum_nights, number_of_reviews, 
                                           reviews_per_month, calculated_host_listings_count,
                                           availability_365)
```

## One hot room type

```{r}
reg_df_2023 = reg_df_2023 %>% mutate(entire = ifelse(room_type == "Entire home/apt",1,0),
                                     private = ifelse(room_type == "Private room",1,0),
                                     shared = ifelse(room_type == "Shared room",1,0),
                                     hotel = ifelse(room_type == "Hotel room",1,0))
reg_df_2023$room_type = NULL
```


# Exploration
## Heatmaps
### 2024

```{r}
cor_matrix_2024 <- cor(reg_df_2024)

# Generate the heatmap
heatmap(cor_matrix_2024, 
        col = colorRampPalette(c("blue", "white", "red"))(50), 
        scale = "none", 
        main = "Heatmap of Correlations")
```

So that's not super helpful.

### 2023

```{r}
cor_matrix_2023 <- cor(reg_df_2023)

# Generate the heatmap
heatmap(cor_matrix_2023, 
        col = colorRampPalette(c("blue", "white", "red"))(50), 
        scale = "none", 
        main = "Heatmap of Correlations")
```

Again, no strong correlations

# Regression

## Model 1 2024
```{r}
model_1_2024 = lm(price ~ ., data = reg_df_2024)
```

### Mod1 summary
```{r}
summary(model_1_2024)
```

### Stepwise selection
```{r}
stepwise_model_2024 <- step(model_1_2024, direction = "both")
```
#### stepwise2024 summary
```{r}
summary(stepwise_model_2024)
```

## Model 1 2023
```{r}
model_1_2023 = lm(price ~ ., data = reg_df_2023)
```

### Mod12023 summary
```{r}
summary(model_1_2023)
```

### Stepwise selection
```{r}
stepwise_model_2023 <- step(model_1_2023, direction = "both")
```

#### stepwise2023 summary
```{r}
summary(stepwise_model_2023)
```

## Model 2 2024
Dropping price outliers for this model
```{r}
reg_min_df_2024 = reg_df_2024 %>% filter(price <= 250000)

model_2_2024 = lm(price ~ ., data = reg_min_df_2024)
```

### Mod2 summary
```{r}
summary(model_2_2024)
```

### Stepwise
```{r}
stepwise_model2_2024 <- step(model_2_2024, direction = "both")
summary(stepwise_model2_2024)
```

## Model 2 2023

```{r}
reg_min_df_2023 = reg_df_2023 %>% filter(price <= 250000)

model_2_2023 = lm(price ~ ., data = reg_min_df_2023)
```

### Mod2 summary
```{r}
summary(model_2_2024)
```

### Stepwise
```{r}
stepwise_model2_2023 <- step(model_2_2023, direction = "both")
summary(stepwise_model2_2023)
```

