---
title: "AirBnB_datasets"
author: "Ellie Schmucker, with edits by Kayla Freeman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load in and process 2024 Datase4t

```{r}
library(tidyverse)
library(skimr)
library(stringr)
library(GGally)

nyc_2024 <- read.csv("nyc_mar2024.csv")


nyc_2024 <- nyc_2024 %>%
  select(id, name, host_id, host_name, neighborhood_overview, neighbourhood_cleansed, neighbourhood_group_cleansed,latitude, longitude, room_type, price, last_scraped, last_review, minimum_nights, number_of_reviews, last_review, reviews_per_month, reviews_per_month, calculated_host_listings_count, availability_365, number_of_reviews_ltm, license, host_location, host_since, host_neighbourhood, host_listings_count, host_total_listings_count,  number_of_reviews_l30d )
head(nyc_2024)

filtered_nyc_2024 <- nyc_2024 %>%
  mutate(last_review_date = as.Date(last_review)) %>%
  filter(last_review_date >= max(last_review_date, na.rm = T) %m-% months(6) )
#
filtered_nyc_2024 %>% select(last_review_date) %>% summary()

head(filtered_nyc_2024$price)
```

## Price to Numeric

```{r}
filtered_nyc_2024$price <- (gsub("\\$", "", filtered_nyc_2024$price))
filtered_nyc_2024$price <- (gsub(",", "", filtered_nyc_2024$price))


filtered_nyc_2024$price = ifelse(filtered_nyc_2024$price == "", 0.00, filtered_nyc_2024$price)

filtered_nyc_2024$price = as.numeric(filtered_nyc_2024$price)

reg_df_2024 = filtered_nyc_2024 %>% select(room_type, price, minimum_nights, number_of_reviews, reviews_per_month, calculated_host_listings_count, availability_365,
                                           neighbourhood_group_cleansed)
```

## One hot room type

```{r}
reg_df_2024 = reg_df_2024 %>% mutate(entire = ifelse(room_type == "Entire home/apt",1,0),
                                     private = ifelse(room_type == "Private room",1,0),
                                     shared = ifelse(room_type == "Shared room",1,0))
reg_df_2024$room_type = NULL
```


# Load in and process 2023 dataset

```{r}
nyc_2023 <- read.csv("nyc_2023.csv")

filtered_nyc_2023 <- nyc_2023 %>%
  mutate(last_review_date = as.Date(last_review)) %>%
  filter(last_review_date >= max(last_review_date, na.rm = T) %m-% months(6) )

filtered_nyc_2023$price = as.numeric(filtered_nyc_2023$price)

reg_df_2023 = filtered_nyc_2023 %>% select(room_type, price, minimum_nights, number_of_reviews, 
                                           reviews_per_month, calculated_host_listings_count,
                                           availability_365, neighbourhood_group)
```

## One hot room type

```{r}
reg_df_2023 = reg_df_2023 %>% mutate(entire = ifelse(room_type == "Entire home/apt",1,0),
                                     private = ifelse(room_type == "Private room",1,0),
                                     shared = ifelse(room_type == "Shared room",1,0))
reg_df_2023$room_type = NULL
```


# Exploration
## Heatmaps
### 2024

```{r}
#cor_matrix_2024 <- cor(reg_df_2024)

# Generate the heatmap
#heatmap(cor_matrix_2024, 
#        col = colorRampPalette(c("blue", "white", "red"))(50), 
#        scale = "none", 
#        main = "Heatmap of Correlations")
```

So that's not super helpful.

### 2023

```{r}
#cor_matrix_2023 <- cor(reg_df_2023)

# Generate the heatmap
#heatmap(cor_matrix_2023, 
#        col = colorRampPalette(c("blue", "white", "red"))(50), 
#        scale = "none", 
#        main = "Heatmap of Correlations")
```

Again, no strong correlations

# Regression

## Model 1 2024
```{r}
model_1_2024 = lm(price ~ ., data = reg_df_2024)
```

### Mod1 summary
```{r}
summary(model_1_2024)
```

### Stepwise selection
```{r}
stepwise_model_2024 <- step(model_1_2024, direction = "both")
```
#### stepwise2024 summary
```{r}
summary(stepwise_model_2024)
```

## Model 1 2023
```{r}
model_1_2023 = lm(price ~ ., data = reg_df_2023)
```

### Mod12023 summary
```{r}
summary(model_1_2023)
```

### Stepwise selection
```{r}
stepwise_model_2023 <- step(model_1_2023, direction = "both")
```

#### stepwise2023 summary
```{r}
summary(stepwise_model_2023)
```

## Model 2 2024
Dropping price outliers for this model
```{r}
reg_min_df_2024 = reg_df_2024 %>% filter(price <= 85000)

model_2_2024 = lm(price ~ ., data = reg_min_df_2024)
```

### Mod2 summary
```{r}
summary(model_2_2024)
```

### Stepwise
```{r}
stepwise_model2_2024 <- step(model_2_2024, direction = "both")
summary(stepwise_model2_2024)
```

## Model 2 2023

```{r}
reg_min_df_2023 = reg_df_2023 %>% filter(price <= 85000)

model_2_2023 = lm(price ~ ., data = reg_min_df_2023)
```

### Mod2 summary
```{r}
summary(model_2_2024)
```

### Stepwise
```{r}
stepwise_model2_2023 <- step(model_2_2023, direction = "both")
summary(stepwise_model2_2023)
```

# Notes So Far

It seems like the predictability of the models is better for 2023, with many of the 2023 significant variables in 2023, becoming insignificant in 2024

# Residual Checking
## Model 1 2024
```{r}
res_1_2024 = residuals(model_1_2024)
for (i in c(1:5)){
  plot(model_1_2024, which = i)
}
```

## Model 1 2024 step
```{r}
for (i in c(1:5)){
  plot(stepwise_model_2024, which = i)
}
```

## Model 2 2024
```{r}
for (i in c(1:5)){
  plot(model_2_2024, which = i)
}
```

## Model 2 2024 step
```{r}
for (i in c(1:5)){
  plot(stepwise_model2_2024, which = i)
}
```

## Model 1 2023
```{r}
for (i in c(1:5)){
  plot(model_1_2023, which = i)
}
```

## Model 1 2023 step
```{r}
for (i in c(1:5)){
  plot(stepwise_model_2023, which = i)
}
```

## Model 2 2023
```{r}
for (i in c(1:5)){
  plot(model_2_2023, which = i)
}
```

## Model 2 2023 step
```{r}
for (i in c(1:5)){
  plot(stepwise_model2_2023, which = i)
}
```


```{r}
min(fitted(model_1_2023))
```

# Model 3

```{r}
reg_fin_df_2024 = reg_min_df_2024 %>% 
  filter(price > 0)

model_3_2024 = glm(price ~ ., data = reg_fin_df_2024)

summary(model_3_2024)
```

```{r}
for (i in c(1:5)){
  plot(model_3_2024, which = i)
}
```

```{r}
reg_fin_df_2024$fitted = fitted(model_3_2024)
reg_fin_df_2024$residual = residuals(model_3_2024)
```

```{r}
stepwise_model3_2024 <- step(model_3_2024, direction = "both")
summary(stepwise_model3_2024)
```



# Model 4

```{r}
reg_m4_df_2024 = reg_fin_df_2024 %>% 
  filter(price > quantile(reg_fin_df_2024$price, 0.01),
         price < quantile(reg_fin_df_2024$price, 0.99),
         availability_365 < 365)

reg_m4_df_2024$log_price = NULL
reg_m4_df_2024$sqrt_price = NULL
reg_m4_df_2024$fitted = NULL
reg_m4_df_2024$residual = NULL


model_4_2024 = glm(log(price) ~ ., data = reg_m4_df_2024)

summary(model_4_2024)
```

```{r}
for (i in c(1:5)){
  plot(model_4_2024, which = i)
}
```

```{r}
stepwise_model4_2024 <- step(model_4_2024, direction = "both")
summary(stepwise_model4_2024)
```

```{r}
for (i in c(1:5)){
  plot(stepwise_model4_2024, which = i)
}
```

## 2023 Model 4

```{r}
reg_m4_df_2023 =  reg_min_df_2023 %>% 
  filter(price > quantile(reg_min_df_2023$price, 0.01),
         price < quantile(reg_min_df_2023$price, 0.99),
         availability_365 < 365)


model_4_2023 = glm(log(price) ~ ., data = reg_m4_df_2023)

summary(model_4_2024)
```

```{r}
for (i in c(1:5)){
  plot(model_4_2023, which = i)
}
```

```{r}
stepwise_model4_2023 <- step(model_4_2023, direction = "both")
```

```{r}
for (i in c(1:5)){
  plot(stepwise_model4_2023, which = i)
}
```

```{r}
summary(stepwise_model4_2023)
summary(stepwise_model4_2024)
```

# Model 4 model comparisons
```{r}

coefs_2024 = data.frame(
  estimates_2024 = coef(stepwise_model4_2024),
  se_2024 = summary(stepwise_model4_2024)$coefficients[, 2]
)

coefs_2023 = data.frame(
  estimates_2023 = coef(stepwise_model4_2023),
  se_2023 = summary(stepwise_model4_2023)$coefficients[, 2]
)


coefficients_df_long <- pivot_longer(coefficients_df, 
                                     cols = c(Model1, Model2), 
                                     names_to = "Model", 
                                     values_to = "Estimate")

# Plot
ggplot(coefficients_df_long, aes(x = Variable, y = Estimate, fill = Model)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_minimal() +
  coord_flip() +
  labs(title = "Comparison of Coefficient Estimates",
       x = "Variables", y = "Estimate")
```



